Alex Iverson

2014-09-29

Designing Mechanisms

\begin{tabular}{|p{5cm}|p{5cm}|}
 \hline
 Analyzed pros and cons of various mechanisms
 &
 Although fairly straight forward, this discussion was also hampered by miscommunications regarding Mechanisms and Subsystems
 \\
 \hline
 Began computing requirements for mechanism
 &
 This is much slower progress than it should be. Most team members’ lack of prior math and physics training means that each calculation has to be accompanied with lessons and explanation
 \\
 \hline
\end{tabular}

We have decided that the mechanisms we want to attempt to build first are a rotating brush intake and a slingshot based lifter. We have divided up into two teams. I am drifting between them, helping explain what we need to do to design them and figure out what parts we need to order before we go out and buy them. My brother is working on the intake; he needs very little guidance. The lifter team, however, has not yet completed a physics class; given how slowly the design and calculations are progressing right now, I will probably have to switch from showing them how to do the calculations to showing them by doing the calculations. I am confident that once we have designs and materials, the other team members will be much more productive. 

Motor load current draw = 0.91A

Motor voltage = 12V

Motor power = $0.91\rm{A}\cdot12\rm{V} = 10.92\rm{W}$

Mass of large ball = 28.9g = 0.0289kg

Density of polycarbonate = $1.22\frac{\rm{g}}{\rm{cm}^3}$

Thickness of plastic = $0.125\rm{in}$ = $0.3175\rm{cm}$

Diameter of large ball = $2.8\rm{in}$ = $7.112\rm{cm}$

$\Delta \rm{height} = 120\rm{cm} = 1.2\rm{m}$

\[\Delta U = m g \Delta h = 0.34\rm{J}\]

\[t = \frac{\Delta U}{P} = 0.031\rm{s}\]

\[f = \frac{1}{t} = 32\rm{Hz}\]

\medskip

What we are doing now would ideally qualify as prototyping, however, it is being executed far too slowly and ponderously to call it such. The scarcity of materials for our team means that we can’t just put together a wood and cardboard mockup to sanity check the ideas. The rest of the team would much rather tinker, and I want to agree, but we do not have all the components required for our ideas on hand, and if we just start buying things without a reasonable idea of what we need then we are likely to run out of money before being able to finish our robot.

Our team name has not been decided yet.
