Ben Trout

2014-10-03

\LaTeX formating for engineering notebook, Promoting FIRST

\begin{tabular}{|p{5cm}|p{5cm}|}
 \hline
 \LaTeX&
 We started our engineering notebook on google docs, but it didn't take us long to realize that it was very confusing and not organized at all. We switched to \LaTeX using Git as our source control system. TexWorks is the editor that we use. 
 \\ 
 \hline
 Promting FIRST&
 We got six tasks as a group to promote our team to the community and get others to hear about our team. Another main purpose for   these six tasks was for obtaining sponsors and others who would want to support our team. 
 \\
 \hline
\end{tabular} 

\section*{\LaTeX}
Due to difficulties with google docs we, as a team, made the decision to switch to \LaTeX. At first I was hesitant as it seemed really hard and inefficient. But after we all learned how to code it, push, and pull the engineering notebook I came to the conclusion that it will be more organized, easy to read, and better to format math. 

\section* {Promoting FIRST}
We have six tasks, one task per person on our team. The six tasks are as follows. Matt is in charge of an essay to get a 3D printer. Filip is in charge of designing on creo a piece we could print using the 3D printer. David is in charge or developing a simple code to move a servo motor to show other people or potential sponsors. Alex is in charge of making a brochure about our team and FIRST to obtain sponsors or to show other people interested in our team or program. Nick is in charge of designing our logo for our team. And finally I am in charge of making a team website to not only promote our team to the greater community, but also promote FIRST. I have a page with example engineering notebooks, a page describing our team, and a page describing our community outreach through out the year. There isn't a whole lot done yet with the website other than the fact that it is created. The website is a build in progress that will be updated throughout the year as we obtain information and do other things. 

Here is a link to our website: https://sites.google.com/a/libertycommon.org/children-of-the-matrix/
  